### 2022-03-09 src/text/3-applications.tex
reorder applications sections
added section in the text requesting multi-insturment figure
reduced multi-instrument figure width to one column
updated subsections

Show some typical and advanced science cases, and refer to published papers

\subsection{Computing Flux points and significance maps}
\label{ssec:1D-3D-analysis}
\input{3.1-std-analysis}

- standard 1D and 3D analysis

See Figure~\ref{fig:fermi_ts_map}.

Ref:~\citep{Stewart2009}

\subsection{Temporal analysis}
\label{ssec:temporal-analysis}
\input{3.2-temporal}
lightcurves and temporal models

\subsection{Multi instrument analysis}
\label{ssec:multi-instrument-analysis}
\todo{Cosimo Nigro}
\begin{figure}[t]
	\centering
	\includegraphics[width=1.\textwidth]{figures/multi_instrument_analysis.pdf}
	\caption{A multi-instrument analysis of the Crab Nebula}
	\label{fig:multi_instrument_analysis} 
\end{figure*}

\subsection{Fitting using physical models}
\label{ssec:naima-models-analysis}
\todo{Cosimo}
\begin{figure*}[t]
(added section in the text requesting multi-insturment figure)

\end{figure}

@@

Talk about simulations here? Or open a new section

>>>>

Gammapy can be used for a variety of science cases by different IACT experiments.
In this section, we show a non-exhaustive list of some typical analysis that be performed.

\subsection{Classical spectral analysis}
\label{ssec:1D-analysis}
\input{3-applications-subsections/3.1-1D-analysis}
\todo{Axel}
A classical spectral analysis using Reflected Regions. Showing flux points, reflected regions on the CTA galactic center data

\subsection{A 3D likelihood analysis}
\label{ssec:1D-analysis}
\input{3-applications-subsections/3.2-3D-analysis}
\todo{Laura}

Simulation of overlapping sources, 3D fitting, npred map, TS maps

\todo{What to do with } Figure~\ref{fig:fermi_ts_map} ?
Ref:~\citep{Stewart2009}

\subsection{Temporal analysis}
\label{ssec:temporal-analysis}
\input{3-applications-subsections/3.3-temporal-analysis}
\todo{Atreyee}
lightcurves and temporal models using the HESS PKS2155

\subsection{Multi instrument analysis}
\label{ssec:multi-instrument-analysis}
\input{3-applications-subsections/3.4-multi-instrument-analysis}
\todo{Cosimo Nigro}
\begin{figure}[t]
	\centering
	\includegraphics[width=1.\textwidth]{figures/multi_instrument_analysis.pdf}
	\caption{A multi-instrument analysis of the Crab Nebula}
	\label{fig:multi_instrument_analysis} 
\end{figure*}

\subsection{Fitting using physical models}
\label{ssec:naima-analysis}
\input{3-applications-subsections/3.5-naima-analysis}
\todo{Cosimo}

Figure \ref{fig:multi_instrument_analysis}. Add explanation text.

@@
